Spatial Population Dynamics

### 2018-07-04 1062_class/eco_model/HW/spatial_PDE/spatial_model.Rmd
up

## Case 1: Population Extinct

$r=0.09, ~ N_{50}(t=0) = 100$

@@

ggplot(df, aes(x=time, y=i, z = N))+
    stat_contour(geom = "polygon", 
                 aes(fill = ..level..),
                 bins = 4000) +
    scale_fill_distiller(palette="Spectral", 
                         trans="log10")+
    geom_contour(aes(colour = ..level..), 
                 binwidth=0.25,
                 lwd=0.3, show.legend = F)+
    scale_color_distiller(palette="Spectral", 
                         trans="log10")+
    labs(x="Time", y="Position", fill="Pop. Size",
         caption= "Diff. between 2 contours = 0.25")+
    theme_bw()
```

@@

$r=0.12, ~ N_{50}(t=0) = 100$

>>>>

## Case 1: Population Extinction

$r=0.09, ~ N_{50}(0) = 100$

@@

ggplot(df, aes(x=time, y=i, z = N))+
    stat_contour(geom = "polygon", 
                 aes(fill = ..level..),
                 bins = 6000) +
    scale_fill_distiller(palette="Spectral", 
                         trans="log10")+
    geom_contour(aes(colour = ..level..), 
                 binwidth=0.25,
                 lwd=0.3, show.legend = F)+
    scale_color_distiller(palette="Spectral", 
                         trans="log10")+
    labs(x="Time", y="Position", fill="Pop. Size",
         caption= "Diff. between 2 contours = 0.25")+
    theme_bw()
```

@@

$r=0.12, ~ N_{50}(0) = 100$
